A Dataset of Operator-client Dialogues Aligned with Database Queries

### 2016-06-28 paper.tex
Sect 3

\vspace{-1.00em}
\subsection{Domain database}
\label{sec:db}

@@

\vspace{-1.00em}
\subsection{Client interface}
\label{sec:client}

The client is asked to request a specific information – a goal from the operator.
He may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and the goals may contradict each other.
For example, the client may at first want a Chinese food, but later it changes her mind and wants to find restaurant serving British food.

Before submitting a reply the client is instructed to read the dialogue history and marked the goals which were presented to the operator as demonstrated in Figure~\ref{fig:client}.
By marking which goals have been already presented to the operator we force the CF workers to pay attention to the dialogue history before submitting their reply.
In Section~\ref{sec:async} we describe how we combine the workers replies to form a~conversations.

\begin{figure}
\vspace{-1.00em}
\begin{center}
\includegraphics[height=30em]{gui-annotators-client}
\caption{Client annotation interface}
\end{center}
\vspace{-1.00em}
\label{fig:client}
\end{figure}
\vspace{-1.00em}

\vspace{-1.00em}
\subsection{Operator interface}
\label{sec:operator}
The operator is asked to politely reply the clients needs according the information stored in the database.
In order to provide the information to clients the operator uses the DB interface depicted in~Figure~\ref{fig:operator}.
Her or she filters the restaurants using a full text search on the database.
The content of the database is intentional hidden if no filter is specified so the filter has to be used.
The CF workers are also instructed explicitly mark the rows of the restaurants about which provide the information in their answer.
Similarly to the client role, an operator does not have to reply to all requested information at once.
It is up to the~worker which information is provided first.

The full text search, our interface to the database, is implemented in Javascript as a simple substring matching over values in the database.
Multiple constrains can be expressed by two substrings separated by a comma.
We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.
The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.

\begin{figure}
\vspace{-1.00em}
\begin{center}
\includegraphics[height=35em]{gui-annotators-system}
\caption{Operator annotation interface}
\end{center}
\vspace{-1.00em}
\label{fig:operator}
\end{figure}
\vspace{-1.00em}

\vspace{-1.00em}
\subsection{Asynchronous collection without real-time responses}
\label{sec:async}
We design the crowdsourcing jobs so the CF contributors are able to work independently to each other.
The roles of client and operator take turns as sets of partial conversations are submitted for collecting a single new response.
As a consequence, a~single conversation is collected from multiple contributors over several job submissions.

Each utterance in conversation may be submitted by different contributor, so contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
The workers are able to mark dialogues which does not make sense and thus they self-assess quality of the conversations.
The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes were said.

We bootstrap the conversation either with an operators introduction "{\it Hello , welcome to the Cambridge restaurant system...}" or we bootstrap the conversation with a~full turn where we add clients greeting e.g. {\it "Hi"} to aforementioned operators utterance.
If we initialize the dialogue with a~full turn the first contributor plays role of the system if we bootstrap the conversation only with~the operators greeting, the contributor plays the client's role.

In a~single job submission, we let the workers append to each dialogue a~single response.
Note also that the conversations are typically rather short so full dialogues are collected after few rounds of submissions.
The workers are paid for every submitted response the same amount independently if they play client or operator role and they typically contribute to multiple conversation during one job submission.
The contributors are assigned roles randomly.

To avoid poor language level of English we restricted the CF worker to English-speaking countries.
We further perform heuristically check for too trivial answers and we added ability to the CF workers to rate each others submission.
It help us filter low quality conversations, but more importantly it motivated workers not to cheat.

>>>>

\vspace{-1.00em}
\subsection{Domain Database}
\label{sec:db}

@@

\vspace{-1.00em}
\subsection{Client Interface}
\label{sec:client}

The CF worker playng the role of the client is asked to request specific information from the operator – a goal.
They may choose not to seek the goal immediately but submit more appropriate response such as greeting instead.
The goals are displayed to the CF worker in the client role gradually turn-by-turn and may contradict each other.
For example, the client may at first want a to find a restaurant serving Chinese food, but later change their mind and seek British food.

Before submitting a reply, the client is instructed to read the dialogue history and mark the goals which were already presented to the operator, as demonstrated in Figure~\ref{fig:client}.\OD{teď nevím, jestli “goal” je celkový cíl, nebo jestli jich má ten worker víc -- to by bylo potřeba jednotně.}
By marking which goals have already been presented to the operator, we force\OD{oblige?} the CF workers to pay attention to the dialogue history before submitting their reply.\OD{do footnotu explicitně vysvětlit, proč to tak je -- proč nemůžou klikat náhodně (že další user vlastně kontroluje toho předchozího tím, že musí zaškrtnout nadmnožinu dříve zaškrtnutých cílů)?}
In Section~\ref{sec:async}, we describe how we combine the workers' replies to form a conversation.\OD{tuhle větu na začátek sekce?}

\begin{figure}[tb] % ať se nemrhá místem
\vspace{-1.00em}
\begin{center}
\includegraphics[height=30em]{gui-annotators-client}
\caption{Client annotation interface}
\end{center}
\vspace{-1.00em}
\label{fig:client}
\end{figure}
\vspace{-1.00em}

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The content of the database is intentionally hidden if no filter is specified so that a filter has to be used to provide results.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

Our full text search interface to the database is implemented in Javascript as a simple substring matching over values in the database.
Multiple constrains can be expressed by two substrings separated by a comma.
We used such a simple interface because it is easy to generate and also reconstruct the candidate results given the query and the database.\OD{co znamená “easy to generate”? hlavně taky “easy to use for untrained CF workers”, to mi přijde důležitější, ne? možná bych ty detaily o tom interfacu hodil rovnou za “using a full text search over the database”}
\ODdel{The CF workers were instructed to mark a candidate row from the results about which they inform in their reply.}\OD{tady se opakuješ}

\begin{figure}[tb]
\vspace{-1.00em}
\begin{center}
\includegraphics[height=35em]{gui-annotators-system}
\caption{Operator annotation interface}
\end{center}
\vspace{-1.00em}
\label{fig:operator}
\end{figure}
\vspace{-1.00em}

\vspace{-1.00em}
\subsection{Asynchronous collection without real-time responses}
\label{sec:async}
We design the crowdsourcing jobs so that the CF contributors are able to work independently of each other.
The roles of client and operator take turns as partial conversations are submitted to CF for collecting a single new response.\OD{přijde mi, že “sets of” to spíš zamlží}
As a consequence, a~single conversation is collected from multiple contributors over several job submissions.

Each utterance in the conversation may be submitted by a different contributor. Therefore, the contributors need to read carefully the dialogue history to understand the conversation before submitting their response.
The workers are able to mark dialogues which do not make sense and thus they self-assess the quality of the conversations.
The contributors mark the conversations as finished if they have no more goals to fulfill and all the goodbyes have been said.

We bootstrap the conversation either with an operator's introduction {\it ``Hello , welcome to the Cambridge restaurant system...''}, or we bootstrap the conversation with a~full turn where we add a client's greeting, e.g., {\it ``Hi''} to the operator's introduction.
If we initialize the dialogue with a~full turn, the first contributor plays role of the system. If we bootstrap the conversation only with~the operator's greeting, the first contributor plays the client's role.

In a~single CF task submission, we let the workers append a~single response to multiple different dialogues, taking on a random role in each of them.
That the conversations are typically rather short \OD{možná rekni počet turnů, ať to nevypadá jako dva} and therefore, full dialogues are collected after few rounds of submissions.
The workers are paid  the same amount of money for every submitted response regardless of whether they play the client or the operator role. \ODdel{and they typically contribute to multiple conversation during one job submission.}\OD{přidal jsem do první věty)}
\ODdel{The contributors are assigned roles randomly.}\OD{ditto}

To avoid poor language level of English, we restricted the CF job to English-speaking countries.
We further perform heuristic checks for too trivial replies, and we enable the CF workers to rate each other's responses.
This help us filter low-quality conversations, but more importantly, it motivates the CF workers not to cheat.
